\thetitle

### 2013-04-13 tfpie/tfpie.tex
finish a draft of 2

\section{Background: the first semester}

@@

  \item the DrRacket programming environment~\cite{dvanhorn:Findler2002DrScheme};

@@

\noindent
We reuses all of these elements in our approach.

@@

@@

\section{Our course}

>>>>

\section{Background: the context at Northeastern}

@@

  \item the DrRacket (formerly DrScheme) 
    programming environment~\cite{dvanhorn:Findler2002DrScheme};

@@

\noindent
We reuse all of these elements in our approach.

@@

These constraints, while in detail specific to Northeastern and the
CCIS curriculum, are broadly similar to the requirements for the first
year at many universities.  Our course also attends to smaller and
more idiosyncratic elements of our curriculum, ranging from formal
reasoning to algorithmic analysis, as described in
section~\ref{sec:our-course}.

@@

\section{Our course}
\label{sec:our-course}
